% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{JiaLuo She}

\basicInfo{
  \email{shejialuo@gmail.com} \textperiodcentered\
  \phone{(+86) 13019582712} \textperiodcentered\
  \github[shejialuo]{https://www.github.com/shejialuo}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Xidian University}, Shaanxi, China}{2021 -- Present}
\textit{Master student} in Software Engineering (SE), expected March 2016
\datedsubsection{\textbf{Chongqing Jiaotong University}, Chongqing, China}{2017 -- 2021}
\textit{B.S.} in Communication Engineering (CE)

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:} C++ == C > Haskell > Go == Js == Python > Java == Scala
  \item \textbf{Platform:} Familiar with Linux system, basic shell script and python programming, able to use basic DevOps tools docker, k8s, istio.
  \item \textbf{Architecture}: Learn about basic distributed systems and parallel computing.
  \item \textbf{Functional}: Learn about basic functional language, master functional programming thinking.
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Embedded System Distributed Cluster Management Technology}}{2012.09 -- 2022.12}
\role{C++, project leader}{Cooperation project of Xi'an Institute of Aeronautical Computing Technology}
For aviation computers, it provides distributed cluster management technologies such as sidecar injection, service discovery, and load balancing.
\begin{itemize}
  \item Imitating k8s, using the concept of admission controller to realize automatic sidecar injection.
  \item Implement polling and region-based load balancing algorithms and threshold-based elastic scaling algorithms.
\end{itemize}

\datedsubsection{\textbf{CS144: Implementing the TCP/IP Protocol Stack}}{2022.06 -- 2022.10}
\role{C++, Linux}{Individual Projects}
Implement the basic TCP/IP protocol stack, https://github.com/shejialuo/CS144
\begin{itemize}
  \item Realize byte stream rearrangement based on the idea of RingBuffer.
  \item A TCP/IP protocol that implements basic functions other than congestion control.
  \item Write implementation ideas: https://luolibrary.com/categories/CS144/
\end{itemize}

\datedsubsection{\textbf{ugit-cpp: A simple git}}{2022.04 -- 2022.10}
\role{C++, Linux}{Individual Projects}
A simple git implementation,https://github.com/shejialuo/ugit-cpp
\begin{itemize}
  \item Imitate git to store blob, tree and commit based on Content-hash.
  \item Implemented basic functionalities such as branching and labeling except remote
\end{itemize}

\datedsubsection{\textbf{CS149: Paral}}{2022.05 -- 2022.12}
\role{C++, CUDA, openMP}{Individual Projects}
https://github.com/shejialuo/CS149-fall21
\begin{itemize}
  \item Use cpp to build a task execution library.
  \item Use cuda to render a graph.
  \item Use openMP to realize BFS for a big graph.
  \item Write ideas: https://luolibrary.com/categories/CS149/
\end{itemize}

\section{\faBook\ technical article}

\datedsubsection{\textbf{Database Systems Complete book solutions}}{2021.12 -- Present}
https://github.com/shejialuo/database-systems-complete-book-solutions

\datedsubsection{\textbf{CS144}}{}
https://luolibrary.com/categories/CS144

\datedsubsection{\textbf{CS149}}{}
https://luolibrary.com/categories/CS149

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Outstanding student cadres of ordinary high schools in Sichuan Province}{2017.03}
\datedline{\textit{Second Prize}, China Undergraduate Mathematical Contest in Modeling}{2019.11}
\datedline{Undergraduate National Scholarships}{2020.12}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https:luolibrary.com
  \item GitHub: https://github.com/shejialuo
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
